Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information

### 2021-08-02 source/jeb_tex/supplementary.tex
Sensitivity analysis included in supplementary info

>>>>

\section{Capillary bridge model: Sensitivity analysis}

Sensitivity analysis was performed using the one-at-a-time (OAT) method. Dimensionless model parameters were initially set to correspond to the ladybug's case, as given by,
contact area fraction ($\alpha=0.1$), pad to hair diameter ratio ($D_p/D_h=50$), hair aspect ratio ($L/D_{h}=10$), water surface tension ratio ($\gamma_{wa}/\gamma_{fa}=3$),
tarsal fluid-water interfacial tension ratio ($\gamma_{fw}/\gamma_{fa}=2$), tarsal fluid size parameter ($\phi_{f}=2$), bubble size parameter ($\phi_{b}=1.6$). Substrate contact angles were kept fixed (same as in main text). Each parameter was varied within a particular range, one at a time, and the corresponding adhesion forces \emph{in air} (F\textsubscript{a}),   \emph{underwater: no bubble} (F\textsubscript{w}) and \emph{underwater: bubble} (F\textsubscript{b}) were calculated. Linear least square regression was performed to quantify the relative change in adhesion for each contact mode with respect to the varied parameter. Here, F\textsubscript{w}/F\textsubscript{a} and F\textsubscript{b}/F\textsubscript{a} were taken to be the model output.
Slope and R\textsuperscript{2} values for each case are reported below (Table \ref{tab:Sens-anal}).

\begin{table}[H]
\begin{tabular}{|l|c|l|l|l|l|l|}
\hline
\multirow{2}{*}{\textbf{Parameter}} & \multirow{2}{*}{\textbf{Range}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Substrate}}} & \multicolumn{2}{c|}{\textbf{F\textsubscript{w}/F\textsubscript{a}}}                                    & \multicolumn{2}{c|}{\textbf{F\textsubscript{b}/F\textsubscript{a}}}                                    \\ \cline{4-7} 
                                    &                                 & \multicolumn{1}{c|}{}                                    & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} \\ \hline
\multirow{2}{*}{$\alpha$}              & \multirow{2}{*}{0.05, 0.3}      & Hydrophilic                                              & 3.03E-18                                  & 1.52E-03                               & 2.30E-01                                  & 7.72E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & -9.69E-17                                 & 3.03E-03                               & -9.40E-01                                 & 7.72E-01                               \\ \hline
\multirow{2}{*}{$D_p/D_h$}             & \multirow{2}{*}{30.0, 60.0}     & Hydrophilic                                              & -8.83E-20                                 & 1.48E-01                               & 1.28E-02                                  & 9.73E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & -5.65E-18                                 & 1.48E-01                               & -1.51E-02                                 & 9.82E-01                               \\ \hline
\multirow{2}{*}{$L/D_{h}$}         & \multirow{2}{*}{8.0, 15.0}      & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & -5.27E-02                                 & 9.11E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & 5.41E-02                                  & 8.66E-01                               \\ \hline
\multirow{2}{*}{$\gamma_{wa}/\gamma_{fa}$}              & \multirow{2}{*}{2.5, 3.5}       & Hydrophilic                                              & -2.01E-01                                 & 8.57E-01                               & -2.43E-01                                 & 9.43E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 4.11E-02                                  & 1.00E+00                               & 6.87E-02                                  & 1.00E+00                               \\ \hline
\multirow{2}{*}{$\gamma_{fw}/\gamma_{fa}$}              & \multirow{2}{*}{1.5, 2.5}       & Hydrophilic                                              & 2.01E-01                                  & 8.62E-01                               & 1.90E-01                                  & 8.94E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 5.56E-01                                  & 1.00E+00                               & 1.57E-01                                  & 1.00E+00                               \\ \hline
\multirow{2}{*}{$\phi_{f}$}             & \multirow{2}{*}{1.7, 2.2}       & Hydrophilic                                              & 1.29E-02                                  & 4.52E-01                               & 6.18E-02                                  & 7.94E-02                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 7.67E-02                                  & 9.84E-01                               & -3.06E-01                                 & 9.66E-01                               \\ \hline
\multirow{2}{*}{$\phi_{b}$}             & \multirow{2}{*}{1.2, 1.8}       & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & -1.14E+00                                 & 8.85E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & 1.46E+00                                  & 9.78E-01                               \\ \hline
\end{tabular}
\caption{Sensitivity analysis \label{tab:Sens-anal}}
\end{table}
